NumPy---Array Programming in Python

### 2020-01-31 body.tex
Update Fig. 1 and 3

Importantly, some projects follow the NumPy API exactly---with Dask,
CuPy, Sparse and JAX the most prominent examples---while others have
NumPy-inspired semantics but, often due to their development history, deviate in places.
% when they deviate, they sometimes fix it, e.g.,
% https://github.com/pytorch/pytorch/pull/1983
% https://github.com/pytorch/pytorch/issues/2228
% many have for numpy users
% https://github.com/torch/torch7/wiki/Torch-for-Numpy-users

@@

  \caption{\textbf{Interoperability.} Through its array protocol, the NumPy API
     can operate on various types of array objects, including those written outside
     of NumPy. In this example, NumPy's \code{sum} function is called on a NumPy and
     a Dask array, respectively. The call succeeds by dispatching to the
     appropriate library implementation, and results in different output array
     types.
  }\label{fig:duck-arrays}

>>>>

Importantly, some projects follow the NumPy API exactly---with Dask,
CuPy, Sparse and JAX the most prominent examples---while others have
NumPy-inspired semantics but, often due to their development history, deviate in places.
Wherever there are such deviations, we often observe users gently requesting,
and developers evolving the software step by step towards the NumPy API,
provided this is possible and reasonable.

% when they deviate, they sometimes fix it, e.g.,
% https://github.com/pytorch/pytorch/pull/1983
% https://github.com/pytorch/pytorch/issues/2228
% many have for numpy users
% https://github.com/torch/torch7/wiki/Torch-for-Numpy-users

@@

  \caption{\textbf{Interoperability.} Through its array protocol, the NumPy API
     can operate on various types of array objects, including those written outside
     of NumPy. In this example, NumPy's \code{sum} function is called on a NumPy and
     a Dask array, respectively. The calls succeed by dispatching to the
     appropriate library implementation, and result in different output array
     types.
  }\label{fig:duck-arrays}
